---
title: "Dplyr and Tidyr lab"
format: html
editor: visual
author : Cédric BAZILE
execute: 
  keep-md: true
  echo: FALSE
---

```{r}
#Setup

here::i_am("Dplyr-Lab---Friday-Group.Rproj")
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
Spt <- readRDS("~/Dauphine/M1 Quantitative Economics/Data Management/Dplyr-Lab---Friday-Group/top-spotify-songs-from-20102019-by-year.Rds")
```

<center>

# Dplyr-Lab (Friday-Group)

</center>

## Exercise 1

### Question 1 : A global perspective on the music scene during the last decade

```{r, results='hide'}
Var_name <- names(Spt)
Var_name

```

```{r}
d_song <- Spt %>% 
  distinct(title,.keep_all = TRUE) %>% 
  nrow()

d_art <- Spt %>% 
  distinct(artist, .keep_all = TRUE) %>% 
  nrow()

d_genre <- Spt %>% 
  distinct(`top genre`, .keep_all = TRUE) %>% 
  nrow()


```

```{r, results='hide'}
#I create some labels to be sure to recognize my data if I forget what it is

library("labelled")
var_label(d_art) <- "Artists (distinct data)"
var_label(d_song) <- "Chansons (distinct data)"
var_label(d_genre) <- "Genre (distinct data)"


```

During the decade, `r d_song` has been produced by `r d_art` artists. `r d_genre` different musical genre inhabit the nightclubs, house and playlists.

### Question 2 : Number of songs per year

```{r}
s_by_y <- Spt %>% 
  distinct(artist,title, .keep_all = TRUE) %>% 
  group_by(year)  %>% 
  summarise("Number of songs" = n())

var_label(s_by_y) <- "Song by year"

s_by_y <- s_by_y %>% 
  rename("Release year" = year)

knitr::kable(s_by_y, caption ="Volume of production", format= "markdown")
```

### Question 3 : Most prolific artist

```{r}
Top_artist <-Spt %>%
  distinct(artist,title, .keep_all = TRUE)%>% 
  group_by(artist)%>% 
  summarise("nsongs" = n()) %>% 
  arrange(desc(nsongs))

top_artist_one <- head(Top_artist, 1)

Top_artist_name <- top_artist_one$artist

Top_artist_ns<- top_artist_one$nsongs

Mysentence <- paste("The  artist producing more songs was", Top_artist_name, "with ", Top_artist_ns, "songs")
cat(Mysentence)
```

### Question 4 : BPM

```{r}
BPM_stats <- Spt %>% 
  distinct(title, .keep_all = TRUE) %>% 
  group_by(`top genre`)%>% 
  summarize("Number of songs"=n(),"Min"=min(bpm), "Mediane"=median(bpm), "Moyenne"=mean(bpm), "Max"=max(bpm), "Sd in percentage"=(sd(bpm)/mean(bpm)))

knitr::kable(BPM_stats, caption ="Statistics on the BPM", format= "markdown")
```

### Question 5 : Energy and Dance ability

```{r}
D_and_en <- Spt %>% distinct(artist,title, .keep_all = TRUE) %>% 
  group_by(year)%>% 
  summarize("Energy"=median(nrgy), "Danceab"=median(dnce))

var_label(D_and_en) <-"Statistiques médianes Dance ability and energy"

knitr::kable(D_and_en, caption = "Key Medians", format = "markdown")


```

### Question 6 :

```{r Median by year}
ggplot(D_and_en, aes(x = year)) +
  geom_line(aes(y = Energy, color = "Energy")) +
  geom_line(aes(y = Danceab, color = "Danceab")) +
  labs(title = "Median By year", x = "Year", y = "Median values", color ="Studied values") +
  theme_minimal()
```

## Exercise 2

```{r Setup, results='hide'}
dropout <- readRDS("~/Dauphine/M1 Quantitative Economics/Data Management/Dplyr-Lab---Friday-Group/dropout.Rds")
Var_name2 <- names(dropout)
Var_name2
```

### Question 1 : Age of enrollement

```{r}
Aoe <- dropout %>% 
  group_by(Gender,`Marital status`) %>% 
  summarise("Median value"=median(`Age at enrollment`))

knitr::kable(Aoe, caption ="Median Age of Enrollment", format= "markdown")


var_label(Aoe)<- "Age of Enrollment by Genre and Marital status"
```

### Question 2 : New tables

```{r}
Aoe_vpiv <- Aoe %>% 
  pivot_wider(names_from = Gender, values_from = `Median value`)

var_label(Aoe_vpiv)<- "Median Age of Enrollment pivoted version"

knitr::kable(Aoe_vpiv, caption ="Median Age of Enrollment (v2)", format= "markdown")
```

### Question 3 : Conditional means

```{r}
Cmeanu <- dropout %>% 
  group_by(Target) %>% 
  summarize(across(starts_with("Curricular units"), mean, na.rm = TRUE))

var_label(Cmeanu)<- "Conditional Mean by Curricular Units"

knitr::kable(Cmeanu, caption="Conditional Mean by Curricular Units", format="markdown")
```

### Question 4 : Pivot
